### 2020-03-08 draft_ABP.tex
Updates from Overleaf

(Chi: I have checked several examples of graph associahedra, there is a conjecture for $u$ variables for this kind of generalized permutohedra: \\
For a element $I$ in the building set $\mathcal{B}$, we define $I_{\text{max}}=\Bigl(\bigcup_{j\sim I} \{j\} \Bigr)\cup I$
where $j\sim I$ means the singleton $j$ is attached to $I$ in the corresponding graph, then 
\begin{equation}
   u_{I} = \prod_{ I \subset J \subset I_{\text{max}}}x_J^{(-1)^{|I|-|J|}}.
\end{equation}
This conjecture can easily be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
)

>>>>

(Chi: I have checked several examples of graph associahedra, there is a conjecture for $u$ variables for this kind of generalized permutohedra: \\
For a element $I$ in the building set $\mathcal{B}$, we define $I_{\text{max}}=\Bigl(\bigcup_{j\sim I} \{j\} \Bigr)\cup I$
where $j\sim I$ means the singleton $j$ is attached to $I$ in the corresponding graph, then 
\begin{equation}
   u_{I} = \prod_{ I \subset J \subset I_{\text{max}}}x_J^{(-1)^{|I|-|J|}}.
\end{equation}
This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
)
